\documentclass[12pt,a4paper,sans]{moderncv}

% ModernCV themes
% \moderncvstyle{classic} % Style options: 'casual', 'classic', 'banking', 'oldstyle'
\moderncvstyle{classic}  % Style options: 'casual', 'classic', 'banking', 'oldstyle'
\moderncvcolor{green}    % Color options: 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'

% Adjust the page margins
\usepackage[scale=0.8]{geometry}
\usepackage{palatino}
\usepackage{xcolor}
\usepackage{hyperref}
% \definecolor{color 1}{ rgb }{0.55 , 0.55 , 0.55}
\colorlet{firstnamecolor}{black!85!blue}
\colorlet{lastnamecolor}{ green!85!black}
\colorlet{titlecolor}{blue!75!black}
\colorlet{sectioncolor}{green!70!black}

% Personal data
\title{Software Engineer} 
\name{Jose de Jesus}
{Herrera Ledon}

\address{Colina San Agustin}{Mexico City, Mexico, 54195} 
\phone[mobile]{+ (52)~5533~428574} 
\email{jesushledon@gmail.com} 
\homepage{www.j3su5pro.com} 
\social[linkedin]{jesusherreraledon}
\social[github]{jesushl}

% Content
\begin{document}
\hypersetup{
    % Colors
    colorlinks=true,
    linkcolor=blue!75!black,
    filecolor=blue,
    urlcolor=blue!75!black,
    % PDF Metadata
    pdftitle={Jose de Jesus Herrera Ledon AI Software Engineer},
    pdfauthor={Jose de Jesus Herrera Ledon},
    pdfsubject={Software Engineer Resume},
    pdfkeywords={AI Engineer, Machine Learning, Python, Intel, Software Development, PyTorch, TorchRec, Full Stack, Quantum Computing, Cloud Computing, Data Science},
    pdfcreator={LaTeX with ModernCV},
    % Display
    pdfpagemode=UseNone,          % No panels (cleaner for CV)
    % Additional metadata 
}


\makecvtitle
\section{Experience}
\cventry{08/2022--Present}{AI Software Engineer}{Intel}{Remote}{}{
    \begin{minipage}[t]{\textwidth}
        \begin{itemize}
            \item Developed and optimized AI frameworks for high-performance computing.
            \item Contributed to open-source projects, enhancing community collaboration.
            \item Implemented gemm XPU for Torchrec, improving performance on Intel GPUs.
            \item VSCode extension development for Intel AI tools, enhancing developer experience.
            \item Lead of Cloud Data Connector library, integrating with various cloud platforms.
            \item Collaboration on Gaudi samples, showcasing AI capabilities on Intel hardware.
        \end{itemize}
    \end{minipage}
}

\cventry{07/2021--08/2022}{Senior Software Engineer}{UMBA}{Mexico City}{}{
    \begin{minipage}[t]{\textwidth}
        \begin{itemize}
            \item Developed and maintained web applications using Flask and TypeScript.
            \item Team lead of customer experience team, focusing on enhancing user engagement.
            \item Creating and maintaining RESTful APIs for transactions and data processing.
            \item Developed internal tools for data analysis and reporting.
            \item Developed customer experience tools, enhancing user engagement and satisfaction.
            \item Collaborate with financial and development teams to ensure compliance and efficiency.
        \end{itemize}
    \end{minipage} 
}
\cventry{11/2019--07/2021}{Senior Software Engineer}{Intel}{Guadalajara, Mexico}{}{
    \begin{minipage}[t]{\textwidth}
        \begin{itemize}
            \item Developed software for quality and business intelligence.
            \item Design and implementation of data pipelines for large-scale data processing.
            \item Add Airflow workflows 
            \item Design and migrate databases using OLAP cubes.
            \item Implement data visualization tools for real-time analytics with django.
        \end{itemize}
    \end{minipage}
}
\cventry{10/2018--07/2019}{Senior Software Engineer}{Contpaqi}{Guadalajara, Mexico}{}{
    \begin{minipage}[t]{\textwidth}
        \begin{itemize}
            \item Working in Research and Technology department.
            \item Developed innovative solutions for financial software.
            \item Create analytics for transactions and user behavior.
            \item Implement machine learning algorithms such as NLP for data analytics.
        \end{itemize}
    \end{minipage}
}
\cventry{08/2016--09/2018}{Team Lead Software Engineer}{HCL Technologies}{Guadalajara, Mexico}{}{
    \begin{minipage}[t]{\textwidth}
        \begin{itemize}
            \item Led a team of software engineers in developing enterprise ML applications.
            \item Implemented Agile methodologies to improve project delivery.
            \item Developed and maintained analytics applications.
            \item Create tools to analyze and improve descriptions for US international Tariff Tables.
        \end{itemize}
    \end{minipage}
}
\cventry{02/2015--08/2016}{Software Developer CI CD}{IBM}{Guadalajara, Mexico}{}{
    \begin{minipage}[t]{\textwidth}
        \begin{itemize}
            \item Collaborated with several teams to implement CI/CD pipelines.
            \item Developed analytics tools and dependency analysis for large codebases.
        \end{itemize}
    \end{minipage}
}
\cventry{07/2014--02/2015}{Software Developer}{Hitts Technologies}{Guadalajara, Mexico}{}{
    \begin{minipage}[t]{\textwidth}
        \begin{itemize}
            \item Developed and maintained enterprise applications using Java for IBM.
            \item Work as L3 support for Rational Jazz Foundation.
        \end{itemize}
    \end{minipage}
}

\section{Skills}

\cvitem{Programming}{Python, Java, JavaScript, C++, SYCL}
\cvitem{AI/ML}{PyTorch,TorchRec, NLP}
\cvitem{Web Dev}{Django, TypeScript, FastAPI, Flask}

\cvitem{Databases}{PostgreSQL, MySQL, MongoDB, Redis}
\cvitem{Tools}{Docker, Kubernetes, Git}
\cvitem{Cloud}{AWS, Azure, GCP}
\cvitem{Other}{Linux, Agile Methodologies, CI/CD}
\cvitem{Languages}{English, Spanish}


\section{Education}
\cventry{2008--2013}{Computer Engineer}{Autonomous University of Mexico}{CDMX}{}{
    \href{http://english.unam.mx/}{View}
}
\cventry{2018}{Machine Learning From Data To Decisions}{MIT Professional Education}{}{}{
    \href{https://www.credential.net/kfzec58v#acc.XgA96V1D}{View Badge}
}
\cventry{2019}{Data Science and Big Data Analytics: Making Data-Driven Decisions}{MIT XPro}{}{}{
    \href{https://certificates.mitxpro.mit.edu/course/89a65334663b4f12ba705077267b94d6.pdf}{View Badge}
}
\cventry{2019}{Quantum algorithms for Cybersecurity, Chemistry and Optimization}{MIT XPro}{}{}{
    \href{https://certificates.mitxpro.mit.edu/course/8a9482946655456eb1be0b78a1dbd7b1.pdf}{View Badge}
}
\cventry{2019}{Quantum Computing Fundamentals}{MIT XPro}{}{}{
    \href{https://certificates.mitxpro.mit.edu/program/06d55e57adbc4fa7b4d981f5abba3d1e.pdf}{View Certificate}
}
\cventry{2019}{Introduction to Quantum Computing }{MIT XPro}{}{}{
    \href{https://certificates.mitxpro.mit.edu/course/c1c5462435aa4a938ef6a6f45acd3678.pdf}{View Badge}
}
\cventry{2025}{Intel Gaudi AI Accelerator}{Intel}{}{}{
    \href{https://www.credly.com/badges/4ee4adea-9c4c-4983-bd5f-549c795eaa1c/linked_in_profile}{View Certificate}
}
\cventry{Current}{Continuous Learning}{Platzi}{}{}{
    \href{https://platzi.com/p/j3su5pro/}{View Courses}
}

\end{document}